Proportional multi-state multiple-cohort life table model

### 2018-04-10 MSLT/MSLTdoc.Rmd
Derived male population numbers from GBD data

ALSO PART OF THE BELOW CODE WILL BE NEEDED FOR THE MSLT AND DISMOD COLLECTION. GENERATE DATA INPUTS FOR DISMOD II FROM HERE.

@@

##Create age categories index in GBDdata (rounding mid age)

@@

##Convert variable val to numberic

@@

##Filter data for England and Greater London adn generate per person rates (per 100,000 in original data)
#England
GBDEngland <- filter(GBDdata, location == "england" & metric == "rate") %>% select(measure, location, sex, age, metric, val, age_cat)

@@

#Greater London (GL)
GBDGL <- filter(GBDdata, location == "greater london" & metric == "rate") %>% select(measure, location, sex, age, metric, val, age_cat)
GBDGL$one_rate <- GBDGL$val/100000

```

>>>>

ALSO PART OF THE BELOW CODE WILL BE NEEDED FOR THE MSLT AND DISMOD COLLECTION. GENERATE DATA INPUTS FOR DISMOD II FROM HERE. These data should be used to generate the general life table and disease life tables

@@

##Create age categories index in GBDdata (rounding mid age), total of 20 age groups

@@

##Create age and sex categories to be able to derive population numbers

GBDdata$sex_age_cat <- paste(GBDdata$age_cat,GBDdata$sex, sep = "_"  )

##Convert variable val to numeric

@@

##Generate a data frame with population numbers for England and Greater London (for life table and Dismod II collection). 
##These are derived from total number of cases and rates per 100,000. To derive values we need to select one cause (E.g. all cause)-does not matter what is chosen.

GBD_England_population_male <- filter(GBDdata, location == "england", measure == "deaths", cause == "all causes", sex == "male", metric == "rate" | metric == "number" ) %>% select(metric, age_cat, val, sex_age_cat)

###Generate population numbers frame males England
 for (i in 1:nrow(GBD_England_population_male)) {
    if (GBD_England_population_male$metric[i] == "number") {
      GBD_England_population_male$val_pop[i] <- GBD_England_population_male$val[i] * 10000/ GBD_England_population_male$val[i + 1]}
   else {GBD_England_population_male$val_pop[i] <- NA}
 }
##Remove rows with zero
GBD_England_population_male <- GBD_England_population_male[!is.na(GBD_England_population_male$val_pop),]

##Last only keep relevant variables

GBD_England_population_male <- filter(GBD_England_population_male) %>% select(age_cat, val_pop)

##Filter data for England and Greater London and generate per person rates (per 100,000 in original data)
#England
GBDEngland <- filter(GBDdata, location == "england" & metric == "rate") %>% select(measure, location, sex, age, metric, val, age_cat)

@@

#Greater London (GL)
GBDGL <- filter(GBDdata, location == "greater london" & metric == "rate") %>% select(measure, location, sex, age, metric, val, age_cat)
GBDGL$one_rate <- GBDGL$val/100000
```
